### 2016-10-20 experiments.tex
Add stats

@@

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{comparegcc}
  \caption{APFD values for GCC suite slices}
  \label{comparegcc}
\end{figure}%

@@

Slicing the tests into 30 random equal-sized groups and using the PLDI 13 best metric (function coverage) and another competitive metric (line coverage), the difference between the repair-based metric and the previous metrics is statistically validated (Figure \ref{comparegcc}).  The differences in APFD values are statistically significant between the mutation-based metric and both function and line coverage, by Wilcoxon test, with $p < 0.002$, and the mean APFD improvement, even for only 37 tests, exposing only 5-11 faults, is still over 3\%.
